\documentclass {beamer}
\mode<presentation>
{
  \usetheme{Pittsburgh}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

\usepackage{amsmath,amsfonts}
\usepackage{graphicx}

\title{Why are we here?}
\subtitle{TBMH's ``Lessons in Bullshit'' Series}
\author{Christopher Wetherill}

\institute[Virginia Polytechnic Institute and State University] % (optional, but mostly needed)
{
  \inst{1}%
  Department of Translational Biology, Medicine, and Health\\
  Virginia Polytechnic Institute and State University
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[PDE 2014] % (optional, should be abbreviation of conference name)
{Professional Development and Ethics, 2014}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{The excretum of large bovine animals}
% This is only inserted into the PDF information catalog. Can be left
% out. 

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

\section{Institutional Approval}

\subsection{Informed Consent}

\begin{frame}{Pants.}{How high can we get them?}
	Exactly how high can we hike our pants? The esteemed Doris T. Zallen is here today to get to the bottom of it. (Here's a hint: not very high. Give it another decade and they'll inch their way up.
\end{frame}

\begin{frame}{Informed consent}
	Don't do things to your subjects that they don't say is okay to do.\\[0.5cm]
	
	\begin{center}
		(Unless it's just really cool. Right?)
	\end{center}
\end{frame}

\begin{frame}{The Dos and Don'ts}{Using accessible language}
	Can you use the first person? Nah, the IRB doesn't like that. [Insert fruity reasons here.] Should you use the word ``saliva''? Nope! What about lactic acid? God, no! Are you stupid? Like, what the hell are you even thinking? I just can't even right now.
\end{frame}

\begin{frame}{Document Length and Layout}
	That long? Ain't nobody got time for that!
\end{frame}

\begin{frame}{Conflicts of Interest}
	Be nice. Don't be mean. Don't be shady. Yay, now we celebrate.
\end{frame}

\begin{frame}{Assent from Children}
	Ooh, why don't we explain it to them using a puppet show? Like, what could be cooler than sticking socks on our hands and making them talk to each other? That'll do the trick!
\end{frame}

\subsection{IRB Approval}

\begin{frame}{Stuff}

\end{frame}

\subsection{IACUC Approval}

\begin{frame}{Stuff}

\end{frame}

\end{document}